Multi-resolution Neural Field Estimation

### 2011-03-07 Multiresolution_framework/ltx/manuscript.tex
added more to my comment about the list of refs
made a few more commends about the block matrix stuff, and caught some typos. Still not sure what we're doing about bold 'r's.

 \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Gamma_3]^{j,i}\label{eq:Upsilon}.

@@

where $[.]_{p,q}$ denotes $\left(p,q\right)$-element of the matrix, and $ [.]^{p,q}$ denotes $\left(p,q\right)$-block of the block matrix and where

@@

 Each $1\times n_{\theta}$ block of $n_x \times n_x$ block matrix $\mathbf U$ is given by

@@

\left[ \mathbf U\right] ^{i,j}&=\int_{\boldsymbol \Omega}\left[\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{j:} dr.

@@

where $[.]_{p:} $ denotes $p^{th}$ row of the matrix. All $n_x^2$ blocks of $\Gamma_1$,$\Gamma_2$ and $\Gamma_3$  can be computed as a once-off before the commencement of the EM iterations. Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation

@@

 \cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}}. \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165]. (This is copy and paste from my thesis ... parham I'll get you the references later)}. \parham{Mike,Ken: can add to this list?}\mike{While I love this kind of thing for a review, I'm not sure we have space for this kind of thing? Also it's not terribly specific.}

>>>>

 \boldsymbol\Upsilon&=T_s\varsigma\sum_{i,j=1}^{n_x}[\boldsymbol\Xi_1]_{i,j}[\Gamma_3]^{j,i}\label{eq:Upsilon}

@@

where $[.]_{p,q}$ denotes the $\left(p,q\right)$-element of the matrix, and $ [.]^{p,q}$ denotes the $\left(p,q\right)$-block of the block matrix and where

@@

Each $1\times n_{\theta}$ block of the $n_x \times n_x$ block matrix $\mathbf U$ is given by \mike{just checking, does $n_x = \mathrm{constant} \times n_\theta$? or is each block $n_x \times n_x$ making $U$ something like $n_x \times n_xn_\theta$? It's probably worth being specific here, making sure that we use the idea of block matrices purely as a mechanism for fancy indexing, rather than treating them as special in some sense.}

@@

\left[ \mathbf U\right] ^{i,j}&=\int_{\boldsymbol \Omega}\left[\mu(r) \right]_i \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) dr'\right]_{j:} dr

@@

\mike{bold $r$s?}where $[.]_{j:} $ denotes the $j^{th}$ row. All $n_x^2$ blocks of $\Gamma_1$,$\Gamma_2$ and $\Gamma_3$  can be computed before the commencement of the EM iterations. Note that to separate $\boldsymbol\theta$ from $\boldsymbol\Lambda_{\theta}$ in forming the $\mathcal{Q}$-function we used the relation

@@

 \cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}}. \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165]. (This is copy and paste from my thesis ... parham I'll get you the references later)}. \parham{Mike,Ken: can add to this list?}\mike{While I love this kind of thing for a review, I'm not sure we have space for this kind of thing? Also it's not terribly specific. I think it's better to stick to how it has the potential to model brains in a manner that rocks, rather than loosely saying it could be applied to any spatiotemporal system, i.e. literally everything.}
